---
title: "Developing Data Products Course Project 1"
author: "Kyriaki Roumpi"
date: "`r Sys.Date()`"
output: html_document
---
# Instructions

Create a web page using R Markdown that features a map created with Leaflet. 

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity! 

# Review criteria

The rubric contains the following two questions:

Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

Does the web page feature an interactive map that appears to have been created with Leaflet?

# My Submission

## Loading the necessary tools

```{r}
library(leaflet)
```

```{r}
library(htmltools)
```

## Loading our data

```{r}
GreekCitiesData <- read.csv("C:/Users/diken/Έγγραφα/R/gr.csv")
```


(File from https://simplemaps.com/data/gr-cities)

We will just use the first 20 cities in Greece, so we will adjust our dataset content, by keeping just the first 20 rows. 

```{r}
GCD <- GreekCitiesData[c(1:20),]
```

The next step is to create a proper data frame easy to manipulate. 


```{r}
GRmap <- data.frame(Ranking = GCD$population,
                     City = GCD$city,
                     Latitude = GCD$lat,
                     Longitude = GCD$lng
)
```

## Finalizing and creating our map

```{r}
map <- GRmap %>%
        leaflet() %>%
        addTiles() %>%
        addMarkers(popup=paste
                ("<br>city: ", htmltools::a(GRmap$city),
                "<br>population: ", formatC(GCD$Ranking, format = "d", big.mark = ",")
                   ) 
        )
```

```{r echo=TRUE}
map
```

